---
title: "Bude, UK"
author: "Alyssa Lai"
date: "4/15/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Bude

Bude is a small seaside resort town in North Cornwall, England, UK, in the civil parish of Bude-Stratton and at the mouth of the River Neet. It is sometimes formerly known as Bude Haven. It lies southwest of Stratton, south of Flexbury and Poughill, and north of Widemouth Bay and is located along the A3073 road off the A39. Bude is twinned with Ergué-Gabéric in Brittany, France. Bude's coast faces Bude Bay in the Celtic Sea, part of the Atlantic Ocean. The population of the civil parish can be found under Bude-Stratton.

***

## Roadmap of Bude

```{r pressure, echo=FALSE}

library(ggmap)

register_google(key = "AIzaSyA0HviPgqohxrKU3qhgBZHUvu1ImGAl5z4")

roads <- get_map(location = c(-4.543678, 50.82664), zoom = 14)
ggmap(roads)

```

***

## Watercolour Map of But

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}

library(ggmap)

register_google(key = "AIzaSyA0HviPgqohxrKU3qhgBZHUvu1ImGAl5z4")

watercolour <- get_map(location = c(-4.543678, 50.82664), zoom = 15, maptype = "watercolor")
ggmap(watercolour)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
